DATA 621 Homework #4

### 2019-11-10 hw4/HW4.Rmd
More work on HW4

@@

```{r, null_prefix = TRUE, comment=NA}
baseline_model <- over_sample_train %>%
  mutate(PRIOR_ACCIDENT = ifelse(OLDCLAIM == 0 & AVG_CLAIM == 0, 0, 1)) %>%
  glm(TARGET_FLAG ~ PRIOR_ACCIDENT, family = binomial(link = "logit"), .)
summary(baseline_model)

results <- test %>%
  mutate(PRIOR_ACCIDENT = ifelse(OLDCLAIM == 0 & AVG_CLAIM == 0, 0, 1)) %>%
  evaluate_model(baseline_model, .)
```

@@

>>>>

## Feature Creation

```{r}
create_features <- function(d){
  d %>%
    mutate(PRIOR_ACCIDENT = ifelse(OLDCLAIM == 0 & AVG_CLAIM == 0, 0, 1)) %>%
    mutate(COLLEGE_EDUCATED = ifelse(EDUCATION %in% c("Bachelors", "Masters", "PhD"), 1, 0)) %>%
    mutate(URBAN_DRIVER = ifelse(URBANICITY == "Highly Urban/ Urban", 1, 0)) %>%
    mutate(YOUNG_MALE = ifelse(SEX == "M" & AGE < 21, 1, 0)) %>%
    mutate(RED_SPORTS_CAR = ifelse(CAR_TYPE == "Sports Car" & RED_CAR == "yes", 1, 0)) %>%
    mutate(HAS_KIDS = ifelse(HOMEKIDS == 0, 0, 1)) %>%
    mutate(KID_DRIVERS = ifelse(KIDSDRIV == 0, 0, 1))
}

over_sample_train <- create_features(over_sample_train)
test <- create_features(test)
```

@@

```{r, null_prefix = TRUE, comment=NA}
baseline_model <- glm(TARGET_FLAG ~ PRIOR_ACCIDENT, family = binomial(link = "logit"), over_sample_train)
summary(baseline_model)

results <- evaluate_model(baseline_model, test)
```

@@

### Risk Taker Model

For this model we are going assume that risk takers are more likely to be in an accident.  To identify those who tend to be risk takers, we are going with the urban legend that those who drive red sports cars are risk takers.  Also young men (16-20) also tend to be risk takers.

```{r, null_prefix = TRUE, comment=NA}
risk_taker_model <- glm(TARGET_FLAG ~ RED_SPORTS_CAR + YOUNG_MALE, family = binomial(link = "logit"), over_sample_train)
summary(risk_taker_model)

risk_taker_results <- evaluate_model(risk_taker_model, test)
```

This model does not have statistically significant predictors, however it has a `r  round(unname(risk_taker_results$overall['Accuracy'])*100,1)`% accuracy rate.  This is because it identified `r  round(unname(risk_taker_results$byClass['Specificity'])*100,1)`% of those who didn't have an accident (and they are more numerous).  When looking at the model's performance on identifying the minority group of interest we see it correcly identified `r round(unname(risk_taker_results$byClass['Sensitivity'])*100,1)`% of the people with accidents.  So while the accuracy rate out preformed the baseline model, this one will not be the model we will use.

### Misc

```{r, null_prefix = TRUE, comment=NA}
model <- glm(TARGET_FLAG ~ CAR_USE, family = binomial(link = "logit"), over_sample_train)
summary(model)

model_results <- evaluate_model(model, test)
```
